On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-09-20 paper2.tex
Last Fabio Version

%  emission to peripheral leptonic emission due to Fermi I or II reacceleration

@@

\begin{keywords}
  Galaxies: clusters - Radio continuum - Gamma rays - X-rays: galaxies: clusters
\end{keywords}

@@

\cite{2011A&A...527A..99E} tried to asses these problems of the classical hadronic 
model by analyzing CR transport processes within a cluster. While CR advection with 
turbulently driven flows results in centrally enhanced CR profiles, the propagation in 
form of CR streaming and diffusion produces a flattening of CR profiles. Hence, 
different CR transport phenomena may also account for the observed bimodality 
of the radio luminosity in the hadronic model and may also explain the spectral 
features observed in some clusters. {\bf This has been recently confirmed 
by \cite{2013arXiv1303.4746W}. In particular, they show that when considering turbulent
damping, CRs can stream at super-Alfvenic velocities, which is crucial
in order to have appreciable CR transport.} 
Note that these phenomena were not considered in earlier analytical works 
(e.g., \citealp{2004A&A...413...17P}) as well as in previous hydrodynamic 
simulations (e.g., \citealp{2001ApJ...562..233M, 
2008MNRAS.385.1211P, 2010MNRAS.409..449P}).
{\bf A satisfactory theory of CR transport in clusters does not exist yet, 
however CR streaming and diffusion may represent an intriguing solution
for the issues of the classical hadronic model.}

Recently, \cite{2012MNRAS.421L.112B} presented the first scaling relations
between RH luminosity and Sunyaev-Zel'dovich (SZ) flux measurements, using the
\emph{Planck} cluster catalogue. While the correlation agrees with previous
scaling measurements based on X-ray data, there is no indication for a bimodal
cluster population dividing clusters into radio-loud and radio-quiet objects at
fixed SZ flux. While the SZ flux correlates tightly with cluster mass, the X-ray
luminosity, $L_\rmn{X}$, exhibits a larger scatter. The CCCs predominantly
populate the high-$L_\rmn{X}$ tail (at any cluster temperature) and make up
approximately half of the radio-quiet objects \citep{2011A&A...527A..99E}. This
suggests that the switch-on/switch-off mechanism may not operate at fixed
$L_\rmn{X}$ but also causes an evolution of that quantity. As the cluster
relaxes after a merger, it cools and forms a denser core. Simultaneously,
$L_\rmn{X}$ is expected to {\em increase} which may simultaneously {\em
  decrease} the radio luminosity owing to the decaying turbulence that is
responsible in maintaining the radio emission in either model (that accounts for
microscopic CR transport). {\bf This has been confirmed by \cite{2013arXiv1307.3049S}
and \cite{2013arXiv1306.4379C}.}

@@

{\bf The main scope of this work is to improve the classical hadronic model with
the inclusion of possible CR transport phenomena, and to make predictions for
future radio surveys. The outline is as follows. In Section~\ref{sec:2.3}, we 
construct a model for the CR proton distribution in clusters that merges results 
of hydrodynamic cluster simulations and an analytical model for microscopic 
CR transport processes. In Section~\ref{sec:3}, we model observed surface 
brightness profiles of individual RHs within the hadronic scenario and explore the 
allowable parameter space for CRs and magnetic fields. Motivated by immanent 
challenges to explain the extent of giant radio halos within the hadronic model, 
we suggest a new hybrid leptonic/hadronic scenario meant to unify the apparently 
distinct classes of giant radio halos, mini halos, and steep spectrum radio sources in 
Section~\ref{sec:discussion_hadronic}. In Section~\ref{sec:4}, we apply our
extended hadronic model to a cosmologically complete mock galaxy cluster 
catalog built from the MultiDark $N$-body $\Lambda$CDM simulation
in \cite{paper1}, hereafter Paper~I. 
We compare the resulting modeled radio-to-X-ray and radio-to-SZ
scaling relations to current observations and show how they vary for different
choices of our CR and magnetic parametrization. In Section~\ref{sec:5}, we show
the radio luminosity functions, compare them to current observational
constraints and provide predictions of the hadronically-generated
RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
our conclusions.} In this work, the cluster mass
$M_{\Delta}$ and radius $R_{\Delta}$ are defined with respect to a density that
is $\Delta=200$ or $\Delta=500$ times the \emph{critical} density of the
Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$,
$\Omega_{\Lambda}=0.7$ and today's Hubble constant of $H_0 = 100 \times
h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

@@

The spatial CR distribution within a galaxy cluster is governed by an interplay
of CR advection, streaming, and diffusion. The advection of CRs by turbulent gas
motions is dominated by the largest eddy turnover time $\tau_{\rmn{tu}}\sim
L_{\rmn{tu}}/ \vel_{\rmn{tu}}$. Here, $L_{\rmn{tu}}$ denotes the turbulent
injection scale (typically of order the core radius) and $\vel_{\rmn{tu}}$ is
the associated turbulent velocity that approaches the sound speed
$\vel_{\rmn{s}}$ for transsonic turbulence after a cluster merger and relaxes to
small velocities afterwards. As a result of advection into the dense cluster
atmosphere, CRs are adiabatically compressed and experience a stratified
distribution in the cluster potential. The gradient of the CR number density
leads to a net CR streaming motion towards the cluster outskirts. Streaming CRs
excite Alfv{\'e}n waves on which they resonantly scatter
\citep{1969ApJ...156..445K}. This isotropizes the CRs' pitch angles, and thereby
reduces the CR bulk speed. Balancing the growth rate of the CR Alfv{\'e}n wave
instability with the wave damping rate due to non-linear Landau damping yields a
CR streaming speed of order the Alfv{\'e}n speed \citep{2001ApJ...553..198F}.
This increases considerably when balancing it with the turbulent damping rate,
which implies an inverse scaling with the CR number density \citep{2013arXiv1303.4746W}.
Once CR streaming depletes the CR number density, this causes a
run-away process with a rapidly increasing streaming speed that even surpasses
the sound speed because the smaller CR number density drives the CR Alfv{\'e}n
wave instability less efficiently. Hence, the crossing time of streaming CRs
over $L_{\rmn{tu}}$ is $\tau_{\rmn{st}}\sim \chi_B\,L_{\rmn{tu}}/
\vel_{\rmn{st}}$ with the streaming velocity given by $\vel_{\rmn{st}}\sim
\vel_{\rmn{s}}$ and $\chi_B\lesssim 1$ parametrizes the magnetic bending scale.
Magnetic bottlenecks for the macroscopic, diffusive CR transport, are critical
in lowering the microscopic streaming velocity of CR by some finite
factor. Therefore, we can define a turbulent propagation parameter
\begin{equation}
  \label{eq:gamma_tu}
  \gamma_{\rmn{tu}}\equiv\frac{\tau_{\rmn{st}}}{\tau_{\rmn{tu}}}=
  \frac{\chi_B\,\vel_{\rmn{tu}}}{\vel_{\rmn{st}}}
\end{equation}
that indicates the relative importance of advection versus CR streaming as the
dominant CR transport mechanism. After a merger, turbulent advective transport
should dominate yielding $\gamma_{\rmn{tu}}\gg 1$, which results in centrally enhanced
CR profiles. In contrast, in a relaxed cluster, CR streaming should be the
dominant transport mechanism implying $\gamma_{\rmn{tu}}\sim1$ and producing
flat CR profiles (for a detailed discussion of these processes, see
\citealp{2011A&A...527A..99E} and \citealp{2013arXiv1303.4746W}).

@@

Recently, \citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
more extended azimuthally averaged RH profile at 352~MHz
\citep{2011MNRAS.412....2B} than the one used in the present study so far
\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
claimed in the Coma RH is somewhat mitigated when considering the negative flux
bowl due to the SZ effect that causes the measured RH spectrum to experience a
sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
pseudo-pressure profiles and assume an accretion shock radius to estimate the
Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
resulting RH spectrum with different spectral indices, $2.1\lesssim
\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
impose a lower floor to the reported uncertainties of 10\% to account for
possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
measurements at different frequencies---in particular for interferometric
measurements that have to reconstruct a large fraction of the flux due to the
``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
found that the SZ decrement at $\sim5$~GHz is below 10\%.
This is clearly in contrast with the results from our simplified approach,
at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
radio halo is significantly larger than what thought before. This could dramatically
impact the estimations regarding the SZ decrement and more sensitive
observations are needed to better clarify this issue. On this, we want to stress once more 
that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
}

@@

As shown by the two model realizations in Fig.~\ref{fig:SBmodeling}, the
(extended) hadronic model cannot account for the total emission at $352$~MHz for
any value in the ($\gamma_{\rmn{tu}}$, $\alpha_{\rmn{B}}$) parameter space; in
agreement with the findings of \citet{2012arXiv1207.3025B}. At the same time,
our analysis at 1.4~GHz confirms the result by \citet{2012...VERITAS} who also
conclude that the hadronic model for the Coma RH is a viable explanation for
magnetic field estimates inferred by Faraday rotation measure studies
\citep{2010A&A...513A..30B} and is not challenged by {\em Fermi} upper limits on
the gamma-ray emission. However, this model agreement is bought at the expense
of flat CR profiles (i.e., {\em low} $\gamma_{\rmn{tu}}$ values) that are
contrary to the expectation of turbulent clusters to host giant radio halos
(i.e., {\em high} $\gamma_{\rmn{tu}}$ values) as proposed by
\citet{2011A&A...527A..99E}. {\bf Note that \cite{2013arXiv1303.4746W} 
arrive at a different conclusion finding that the increase of turbulence promotes 
outward streaming more than inward advection, therefore allowing flat CR 
distributions in turbulent clusters. However, this does not help in, e.g.,
the case of the 352~MHz data, where, as discussed above, not even a
flat CR profile is enough to explain the observed emission within the
hadronic scenario.} These finding hint at the necessity of a second,
leptonic component (within the general framework of the hadronic model) that
fills in the patchier emission in the peripheral, low-surface brightness regions
of the halo, in particular at low frequencies \cite[see Fig.~3
of][]{2011MNRAS.412....2B}. We will return to this point in
Section~\ref{sec:discussion_hadronic}.

@@

In order to cleanly assess the possibility of the hadronic model to alone
explain the RH data, we only considered the hadronically-induced radio 
emission component in the preceding section. Hence, by construction, we 
neglected other (leptonic) emission components, such as re-accelerated electrons. 
{\bf Possible biases that may affect our previous conclusions are the following.}

@@

\subsubsection{Halo switch-on/-off mechanism and the radio-X-ray bimodality.}
  Clearly, a cluster merger injects turbulence and shocks that could both
  accelerate fossil electrons and switch the leptonic component on. On the other
  hand, CR advection produces centrally enhanced CR profiles because of adiabatic
  compression of CRs for radial eddies. The energetization and transport of
  CRs to the central halo regions implies a lightening up of the hadronic
  emission component. For the leptonic component,
  the halo switch off is faster or comparable to the dynamical time scale,
  $t_{\rm dyn} \sim t_{\rm H}/\sqrt{\Delta} \sim 1 \,\rmn{Gyr}
  \Delta_{100}^{-1/2}$, where $t_{\rm H}=10$~Gyr,
  $\Delta_{100}=\rho/(100\bar{\rho})$. In case of diffusive shock acceleration
  of fossil electrons, the radio emission will be shut off within a CR electron
  cooling time ($t_\rmn{cool}\sim100$~Myr) if the acceleration source ceases,
  i.e., when shocks have dissipated all the energy. In the case of the turbulent
  re-acceleration model, the turbulence decays on a few eddy turnover time
  scales on the injection scale which should take only somewhat longer. The
  hadronic emission component is also expected to decrease substantially once
  turbulent pumping of CRs ceases and CRs are set free to stream, which results
  in a net CR flux towards the external cluster regions. The accompanying
  flattening of the CR profile implies a lowering of the hadronic radio emission
  because the CRs see a smaller target density in the outer parts. 
  {\bf Additionally, \cite{2013arXiv1303.4746W} found that turbulence seems 
  to promote outward streaming more than inward advection, suggesting the 
  possibility to substantially decrease the radio flux even in merging clusters.} 
  This should lead naturally to a bimodality of radio synchrotron emissivities due to
  hadronic and leptonic halo components.

@@

{\bf In the following, we apply our model to the complete
cosmological mock cluster catalog build from the MultiDark $N$-body 
simulation in our Paper~I. For each object in the sample, we mainly use
the information on its mass, radius and phenomenologically assigned 
ICM gas density to calculate the radio (and gamma-ray) emission.}

@@

The slope of our model depends on the different parameter choices and,
particularly, on the relative differences introduced for the NCCC/CCC and 
the radio-loud/quiet populations. However, we note that our
$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ is slightly shallower than the 
observed relation, more similar to the \cite{2009JCAP...09..024K} prediction.
{\bf The same apply to the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling relation. 
Potentially, this may hint at the contribution of a second, leptonic component
that would steepen the slope of our model scaling relation at high mass.
In particular, the finding of \cite{2013arXiv1306.4379C} that clusters do 
seem to show a bimodaily at very high $Y_{\rmn{SZ}}$ may also be an hint 
of an increasingly important leptonic component.} 
{\bf However, we do not expect this component to alter significantly our conclusions
regarding the luminosity functions of next sections for two main reasons. (i) It would be present 
only in the radio-loud merging NCCC sample, the radio (giant) halos. And (ii) it would be dominant only 
at very high masses because the dissipated energy that is available for energizing fossil electrons should 
be a fraction of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
magneto-turbulent re-acceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
of our mock sample, only $31$ radio-loud \mbox{NCCCs} are found for $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, 
where, e.g., turbulent reaccelerated RHs lie according to \cite{2010A&A...509A..68C}.

@@

This represent just a phenomenological fudge aiming to reproduce what 
expected by turbulent re-acceleration $L_{1.4~\rmn{GHz}} \sim M_{500}^4$ 
\citep{2007MNRAS.378.1565C,2013arXiv1306.4379C}.
It is tied to the underling hadronic component such that we can use as
guidance the results obtained with the surface brightness modeling
on the missing signal fraction. Additionally, in this way, it is tied to the
CR and B properties of a given cluster.  
As $L_{1.4~\rmn{GHz, had}} \sim M_{500}^{1.7}$,
we add an additional mass scaling to reach the
desired $L_{1.4~\rmn{GHz}} \sim M_{500}^4$.
The resulting median (mean) boost is about
32\% (47\%) of the hadronic component.\footnote{The modeling of
   Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
   may be necessary. Note however that if we would allow flat CR profiles 
   in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
   the required fraction of leptonic component could be smaller.} 
The boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
corresponding scaling relations have slopes close to the ones of 
the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ 
observational samples, respectively.}

@@

{\bf We introduce a phenomenological realization of the additional leptonic component in an hybrid scenario,
and show how this can affect the population of high-mass radio-loud NCCCs (radio giant halos), bringing 
its scaling relations in agreement with the the available observational samples. However, due to the nature of 
our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few tens of objects 
would be affected by such a correction. These are not statistically significant against our 
whole sample and, therefore, we refrain from adding this component in the analysis
of the luminosity functions and in making predictions for future surveys.}

>>>>

%  emission to peripheral leptonic emission due to Fermi I or II re-acceleration

@@

\begin{keywords}
  Galaxies: clusters - Radio continuum - Gamma rays
\end{keywords}

@@

\cite{2011A&A...527A..99E} tried to asses these problems of the classical hadronic 
model by analyzing CR transport processes within a cluster. While CR advection with 
turbulently driven flows results in centrally enhanced CR profiles, the propagation in 
form of CR streaming and diffusion produces a flattening of CR profiles. Hence, 
different CR transport phenomena may also account for the observed bimodality 
of the radio luminosity in the hadronic model and may also explain the spectral 
features observed in some clusters. {\bf This has been recently confirmed 
by \cite{2013arXiv1303.4746W}. In particular, they show that when considering turbulent
damping, CRs can stream at super-Alfvenic velocities.} 
Note that these phenomena were not considered in earlier analytical works 
(e.g., \citealp{2004A&A...413...17P}) as well as in previous hydrodynamic 
simulations (e.g., \citealp{2001ApJ...562..233M, 
2008MNRAS.385.1211P, 2010MNRAS.409..449P}).
{\bf A satisfactory theory of CR transport in clusters does not exist yet, 
however CR streaming and diffusion may represent an intriguing solution
for the issues of the classical hadronic model.}

\cite{2012MNRAS.421L.112B} presented the first scaling relations
between RH luminosity and Sunyaev-Zel'dovich (SZ) flux measurements, using the
\emph{Planck} cluster catalogue. While the correlation agrees with previous
scaling measurements based on X-ray data, there is no indication for a bimodal
cluster population dividing clusters into radio-loud and radio-quiet objects at
fixed SZ flux. While the SZ flux correlates tightly with cluster mass, the X-ray
luminosity, $L_\rmn{X}$, exhibits a larger scatter. The CCCs predominantly
populate the high-$L_\rmn{X}$ tail (at any cluster temperature) and make up
approximately half of the radio-quiet objects \citep{2011A&A...527A..99E}. This
suggests that the switch-on/switch-off mechanism may not operate at fixed
$L_\rmn{X}$ but also causes an evolution of that quantity. As the cluster
relaxes after a merger, it cools and forms a denser core. Simultaneously,
$L_\rmn{X}$ is expected to {\em increase} which may simultaneously {\em
  decrease} the radio luminosity owing to the decaying turbulence that is
responsible in maintaining the radio emission in either model (that accounts for
microscopic CR transport). {\bf This has been recently confirmed by 
\cite{2013arXiv1307.3049S} and \cite{2013arXiv1306.4379C}.}

@@

{\bf The main scope of this work is to upgrade the classical hadronic model with
the inclusion of possible CR transport phenomena, and to make predictions for
future radio surveys. The outline is as follows. In Section~\ref{sec:2.3}, we 
construct a model for the CR proton distribution in clusters that merges results 
of hydrodynamic cluster simulations and an analytical model for microscopic 
CR transport processes. In Section~\ref{sec:3}, we model observed surface 
brightness profiles of individual RHs within the hadronic scenario and explore the 
allowable parameter space for CRs and magnetic fields. Motivated by immanent 
challenges to explain the extent of giant radio halos within the hadronic model, 
we suggest a new hybrid leptonic/hadronic scenario meant to unify the apparently 
distinct classes of giant radio halos, mini halos, and steep spectrum radio sources in 
Section~\ref{sec:discussion_hadronic}. In Section~\ref{sec:4}, we apply our
extended hadronic model to a cosmologically complete mock galaxy cluster 
catalog built from the MultiDark $N$-body $\Lambda$CDM simulation
in \cite{paper1}, hereafter Paper~I. 
We compare the resulting modeled radio-to-X-ray and radio-to-SZ
scaling relations to current observations and show how they vary for different
choices of our CR and magnetic field parametrizations. In Section~\ref{sec:5}, we show
the radio luminosity functions, compare them to current observational
constraints, and provide predictions of the hadronically-generated
RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
our conclusions.} In this work, the cluster mass
$M_{\Delta}$ and radius $R_{\Delta}$ are defined with respect to a density that
is $\Delta=200$ or $\Delta=500$ times the \emph{critical} density of the
Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$,
$\Omega_{\Lambda}=0.7$ and today's Hubble constant of $H_0 = 100 \times
h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

@@

The spatial CR distribution $C(R)$ within a galaxy cluster is governed by an interplay
of CR advection, streaming, and diffusion. The advection of CRs by turbulent gas
motions is dominated by the largest eddy turnover time $\tau_{\rmn{tu}}\sim
L_{\rmn{tu}}/ \vel_{\rmn{tu}}$. Here, $L_{\rmn{tu}}$ denotes the turbulent
injection scale (typically of order the core radius) and $\vel_{\rmn{tu}}$ is
the associated turbulent velocity that approaches the sound speed
$\vel_{\rmn{s}}$ for transsonic turbulence after a cluster merger and relaxes to
small velocities afterwards. As a result of advection into the dense cluster
atmosphere, CRs are adiabatically compressed and experience a stratified
distribution in the cluster potential. The gradient of the CR number density
leads to a net CR streaming motion towards the cluster outskirts. Streaming CRs
excite Alfv{\'e}n waves on which they resonantly scatter
\citep{1969ApJ...156..445K}. This isotropizes the CRs' pitch angles, and thereby
reduces the CR bulk speed. Balancing the growth rate of the CR Alfv{\'e}n wave
instability with the wave damping rate due to non-linear Landau damping yields a
CR streaming speed of order the Alfv{\'e}n speed \citep{2001ApJ...553..198F}.
This increases considerably when balancing it with the turbulent damping rate,
which implies an inverse scaling with the CR number density \citep{2013arXiv1303.4746W}.
Once CR streaming depletes the CR number density, this causes a
run-away process with a rapidly increasing streaming speed that even surpasses
the sound speed because the smaller CR number density drives the CR Alfv{\'e}n
wave instability less efficiently. Hence, the crossing time of streaming CRs
over $L_{\rmn{tu}}$ is $\tau_{\rmn{st}}\sim \chi_B\,L_{\rmn{tu}}/
\vel_{\rmn{st}}$ with the streaming velocity given by $\vel_{\rmn{st}}\sim
\vel_{\rmn{s}}$ and $\chi_B\lesssim 1$ parametrizes the magnetic bending scale.
Magnetic bottlenecks for the macroscopic, diffusive CR transport, are critical
in lowering the microscopic streaming velocity of CR by some finite
factor. Therefore, we can define a turbulent propagation parameter
\begin{equation}
  \label{eq:gamma_tu}
  \gamma_{\rmn{tu}}\equiv\frac{\tau_{\rmn{st}}}{\tau_{\rmn{tu}}}=
  \frac{\chi_B\,\vel_{\rmn{tu}}}{\vel_{\rmn{st}}}
\end{equation}
that indicates the relative importance of advection versus CR streaming as the
dominant CR transport mechanism. After a merger, turbulent advective transport
should dominate yielding $\gamma_{\rmn{tu}}\gg 1$, which results in centrally enhanced
CR profiles. In contrast, in a relaxed cluster, CR streaming should be the
dominant transport mechanism implying $\gamma_{\rmn{tu}}\sim1$ and producing
flat CR profiles (for a detailed discussion of these processes, see
\citealp{2011A&A...527A..99E} and \citealp{2013arXiv1303.4746W}).

@@

\citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
more extended azimuthally averaged RH profile at 352~MHz
\citep{2011MNRAS.412....2B} than the one used in the present study so far
\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
claimed in the Coma RH is somewhat mitigated when considering the negative flux
bowl due to the SZ effect that causes the measured RH spectrum to experience a
sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
pseudo-pressure profiles and assume an accretion shock radius to estimate the
Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
resulting RH spectrum with different spectral indices, $2.1\lesssim
\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
impose a lower floor to the reported uncertainties of 10\% to account for
possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
measurements at different frequencies---in particular for interferometric
measurements that have to reconstruct a large fraction of the flux due to the
``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
found that the SZ decrement at $\sim5$~GHz is below 10\%.
This is clearly in contrast with the results from our simplified approach,
at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
radio halo is significantly larger than what thought before. This could dramatically
impact the estimations regarding the SZ decrement and more sensitive
observations are needed to better clarify this issue. On this, we want to stress once more 
that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
}

@@

As shown by the two model realizations in Fig.~\ref{fig:SBmodeling}, the
(extended) hadronic model cannot account for the total emission at $352$~MHz for
any value in the ($\gamma_{\rmn{tu}}$, $\alpha_{\rmn{B}}$) parameter space; in
agreement with the findings of \citet{2012arXiv1207.3025B}. At the same time,
our analysis at 1.4~GHz confirms the result by \citet{2012...VERITAS} who also
conclude that the hadronic model for the Coma RH is a viable explanation for
magnetic field estimates inferred by Faraday rotation measure studies
\citep{2010A&A...513A..30B} and is not challenged by {\em Fermi} upper limits on
the gamma-ray emission. However, this model agreement is bought at the expense
of flat CR profiles (i.e., {\em low} $\gamma_{\rmn{tu}}$ values) that are
contrary to the expectation of turbulent clusters to host giant radio halos
(i.e., {\em high} $\gamma_{\rmn{tu}}$ values) as proposed by
\citet{2011A&A...527A..99E}. {\bf Note that \cite{2013arXiv1303.4746W} 
arrive at a different conclusion finding that the increase of turbulence promotes 
outward streaming more than inward advection, therefore allowing flat CR 
distributions in turbulent clusters. However, this does not help in
the case of the 352~MHz data, where, as discussed above, not even a
flat CR profile is enough to explain the observed emission within the
hadronic scenario.} These finding hint at the necessity of a second,
leptonic component (within the general framework of the hadronic model) that
fills in the patchier emission in the peripheral, low-surface brightness regions
of the halo, in particular at low frequencies \cite[see Fig.~3
of][]{2011MNRAS.412....2B}. We will return to this point in
Section~\ref{sec:discussion_hadronic}.

@@

In order to cleanly assess the possibility of the hadronic model to alone
explain the RH data, we only considered the hadronically-induced radio 
emission component in the preceding section. Hence, by construction, we 
neglected other (leptonic) emission components, such as reaccelerated electrons. 
{\bf Possible biases that may affect our previous conclusions are the following.}

@@

\subsubsection{Halo switch-on/-off mechanism and the radio-X-ray bimodality.}
  Clearly, a cluster merger injects turbulence and shocks that could both
  accelerate fossil electrons and switch the leptonic component on. On the other
  hand, CR advection produces centrally enhanced CR profiles because of adiabatic
  compression of CRs for radial eddies. The energetization and transport of
  CRs to the central halo regions implies a lightening up of the hadronic
  emission component. For the leptonic component,
  the halo switch off is faster or comparable to the dynamical time scale,
  $t_{\rm dyn} \sim t_{\rm H}/\sqrt{\Delta} \sim 1 \,\rmn{Gyr}
  \Delta_{100}^{-1/2}$, where $t_{\rm H}=10$~Gyr,
  $\Delta_{100}=\rho/(100\bar{\rho})$. In case of diffusive shock acceleration
  of fossil electrons, the radio emission will be shut off within a CR electron
  cooling time ($t_\rmn{cool}\sim100$~Myr) if the acceleration source ceases,
  i.e., when shocks have dissipated all the energy. In the case of the turbulent
  re-acceleration model, the turbulence decays on a few eddy turnover time
  scales on the injection scale which should take only somewhat longer. The
  hadronic emission component is also expected to decrease substantially once
  turbulent pumping of CRs ceases and CRs are set free to stream, which results
  in a net CR flux towards the external cluster regions. The accompanying
  flattening of the CR profile implies a lowering of the hadronic radio emission
  because the CRs see a smaller target density in the outer parts. 
  {\bf Additionally, \cite{2013arXiv1303.4746W} found that turbulence seems 
  to promote outward streaming more than inward advection, suggesting the 
  possibility to substantially decrease the radio flux also in merging clusters.} 
  This should lead naturally to a bimodality of radio synchrotron emissivities due to
  hadronic and leptonic halo components.

@@

{\bf In the following, we apply our model to the complete
cosmological mock cluster catalog build from the MultiDark $N$-body 
simulation in our Paper~I. For each object in the sample, we mainly use
the information on its mass and phenomenologically assigned 
ICM gas density to calculate the radio (and gamma-ray) emission.}

@@

The slope of our model depends on the different parameter choices and,
particularly, on the relative differences introduced for the NCCC/CCC and 
the radio-loud/quiet populations. However, we note that our
$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ is slightly shallower than the 
observed relation, more similar to the \cite{2009JCAP...09..024K} prediction.
{\bf The same apply to the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling relation. 
Potentially, this may hint at the contribution of a second, leptonic component
that would steepen the slope of our model scaling relation at high mass.
In particular, the finding of \cite{2013arXiv1306.4379C} that clusters do 
seem to show a bimodaily at very high $Y_{\rmn{SZ}}$ may also be an hint 
of an increasingly important leptonic component.} 
{\bf However, we do not expect this component to alter significantly our conclusions
regarding the luminosity functions of next sections for two main reasons. (i) It would be present 
only in the radio-loud merging NCCC sample, i.e., the radio (giant) halos. And (ii) it would be dominant only 
at very high masses because the dissipated energy that is available for energizing fossil electrons should 
be a fraction of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
magneto-turbulent re-acceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
of our mock sample, only $31$ radio-loud \mbox{NCCCs} are found for $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, 
where, e.g., turbulent reaccelerated RHs lie according to \cite{2010A&A...509A..68C}.

@@

We stress that this is just a phenomenological correction factor aiming to reproduce what 
expected by turbulent re-acceleration $L_{1.4~\rmn{GHz}} \sim M_{500}^4$ 
\citep{2007MNRAS.378.1565C,2013arXiv1306.4379C}.
It is tied to the underling hadronic component such that we can use as
guidance the results on the missing signal fraction obtained with the 
surface brightness modeling. Additionally, in this way, it is tied to the
CR and magnetic field properties of a given cluster.  
As $L_{1.4~\rmn{GHz, had}} \sim M_{500}^{1.7}$,
we adopt an additional mass scaling to reach the
desired $L_{1.4~\rmn{GHz}} \sim M_{500}^4$.
The resulting median (mean) boost is about
32\% (47\%) of the hadronic component.\footnote{{\bf The modeling of
   Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
   may be necessary. Note however that if we would allow flat CR profiles 
   in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
   the required fraction of leptonic component could be smaller.}} 
The boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
corresponding scaling relations have slopes close to the ones of 
the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ 
observational samples, respectively.}

@@

{\bf We consider an example of a phenomenological correction factor representing the 
additional leptonic component in an hybrid scenario. We show how this can affect the 
population of high-mass radio-loud NCCCs, i.e, the giant halos, bringing its scaling relations 
in agreement with the the available observational samples. However, due to the nature 
of our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few 
tens of objects would be affected by such a correction. These are not statistically significant 
against our whole sample and, therefore, we refrain from adding this component in the 
subsequent analysis, leaving its theoretical modeling to future work.}
